Towards the Analysis of the Queuing System Operating in~the~Random Environment with Resource Allocation

### 2019-09-22 article.tex
Add researcherid and scopus author id
fix compilation

@@

% \received{\formatdate{09}{10}{2018}}

\begin{authordescription}
% \authorfull[russian]{Зарядов Иван Сергеевич}
\authorfull[english]{Zaryadov, Ivan S.}
% \authordegree[russian]{кандидат физико\-/математических наук}
\authordegree[english]{Candidate of Physical and Mathematical Sciences}
% \authorpost[russian]{доцент кафедры прикладной информатики и теории вероятностей РУДН, старший научный сотрудник ИПИ ФИЦ ИУ РАН}
\authorpost[english]{assistant professor of   Department of Applied
   Probability  and Informatics of  Peoples' Friendship
    University of Russia (RUDN University); Senior Researcher of
    Institute of Informatics Problems of 
  Federal Research Center ``Computer Science and Control'' 
  Russian Academy of Sciences}
\email{zaryadov-is@rudn.ru}
\orcid{0000-0002-7909-6396}
\phone{+7(495)9550927}
\end{authordescription}

@@

\abstracts{ The mathematical model of the system, that consists of a
  storage device and several homogeneous servers and operates in a
  random environment, and provides incoming applications not only
  services, but also access to resources of the system, is being
  constructed.  The random environment is represented by two
  independent Markov processes.  The first of Markov processes
  controls the incoming flow of applications to the system and the
  size of resources required by each application. The incoming flow is
  a Poisson one, the rate of the flow and the amount of resources
  required for the application are determined by the state of the
  external Markov process. The service time for applications on
  servers is exponential distributed. The service rate and the maximum
  amount of system resources are determined by the state of the second
  external Markov process. When the application leaves the system, its
  resources are returned to the system. In the system under
  consideration, there may be failures in accepting incoming
  applications due to a lack of resources, as well as loss of the
  applications already accepted in the system, when the state of the
  external Markov process controlling the service and provision of
  resources changes.  A random process describing the functioning of
  this system is constructed. The system of equations for the
  stationary probability distribution of the constructed random
  process is presented in scalar form. The main tasks for further
  research are formulated.  }

@@

%\thanks{The publication has been prepared with the support of the
%  ``RUDN University Program 5-100'' and funded by RFBR according to
%  the research projects No.~18-07-00692 and No.~16-07-00766.}

>>>>

\pacs{%
  07.05.Tp, %Computer modeling and simulation                                                                                                                                
  02.60.Pn, %Numerical optimization                                                                                                                                          
  02.70.Bf %Finite-difference methods                                                                                                                                        
}

\documentType{Research article}
% жанр (тип) каждой публикации на русском и английском языке:
% - Научная статья/Research article;
% - Обзорная статья/Review;
% - Редакционная статья/Editorial;
% - Рецензия на книгу/Book Review;
% - Информационная статья/Information article

@@

% \received{29}{06}{2019}
% \accepted{30}{06}{2019}

\begin{authordescription}
  % \authorfull[russian]{Зарядов Иван Сергеевич}
  \authorfull[english]{Zaryadov, Ivan S.}
  % \authordegree[russian]{кандидат физико\-/математических наук}
  \authordegree[english]{Candidate of Physical and Mathematical Sciences}
  % \authorpost[russian]{доцент кафедры прикладной информатики и теории вероятностей РУДН, старший научный сотрудник ИПИ ФИЦ ИУ РАН}
  \authorpost[english]{assistant professor of   Department of Applied
    Probability  and Informatics of  Peoples' Friendship
    University of Russia (RUDN University); Senior Researcher of
    Institute of Informatics Problems of
    Federal Research Center ``Computer Science and Control''
    Russian Academy of Sciences}
  \email{zaryadov-is@rudn.ru}
  \orcid{0000-0002-7909-6396}
  \researcherid{B-8154-2018}
  \scopusauthorid{35294470000}
  \phone{+7(495)9550927}
\end{authordescription}

@@

\abstracts{%
  The mathematical model of the system, that consists of a
  storage device and several homogeneous servers and operates in a
  random environment, and provides incoming applications not only
  services, but also access to resources of the system, is being
  constructed.  The random environment is represented by two
  independent Markov processes.  The first of Markov processes
  controls the incoming flow of applications to the system and the
  size of resources required by each application. The incoming flow is
  a Poisson one, the rate of the flow and the amount of resources
  required for the application are determined by the state of the
  external Markov process. The service time for applications on
  servers is exponential distributed. The service rate and the maximum
  amount of system resources are determined by the state of the second
  external Markov process. When the application leaves the system, its
  resources are returned to the system. In the system under
  consideration, there may be failures in accepting incoming
  applications due to a lack of resources, as well as loss of the
  applications already accepted in the system, when the state of the
  external Markov process controlling the service and provision of
  resources changes.  A random process describing the functioning of
  this system is constructed. The system of equations for the
  stationary probability distribution of the constructed random
  process is presented in scalar form. The main tasks for further
  research are formulated.
}

@@
